Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-07 icdm/submission/includes/evaluation.tex
summary better
s

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will compare our embeddings to a human judged dataset of pairs of words based on their similarity. The reader was also given an explanation about the configuration of our network and input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.

>>>>

To summarize, we deleted words that appear very often (subsampling) and very infrequently (min count) from our dataset, i.e text8 dataset. To evaluate our word embeddings we defined the cosine distance and will measur the quality our embeddings by comparing theim  to a human judged dataset of word pairs, based on their similarity. The reader was also given an explanation about the configuration of our network and introduced to the concept of input shuffling. With all this knowledge we can know present the achieved experimental results in the next section.
